Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-04-07 documents/TriangleScenarioArXiv/ts.tex
fixed dozens of typos and shortened several sections, namely the appendix on symmetries

    The manuscript is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used. \Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities. \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure was chosen as a case study. \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}. The Fritz distribution was proven to be non-classical without the use of inequalities --- this report fills in the desired missing inequalities. A sample of these inequalities are presented in \cref{sec:found_inequalities} (specifically \cref{eq:ww_ineq} as well as in \cref{eq:web_inequality,eq:symmetic_web_inequality}\todo[TC]{Reorganize the location of the inequalities}). \Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the specific context of this work. Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}. \Cref{sec:deriving_inequalities} demonstrates how the inflation technique can be used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions. Finally, \cref{sec:violations_noise} introduces the method for parameterizing the space of quantum-accessible distributions which we used to numerically optimize against our derived inequalities in search of stronger types of non-classicality. Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities. \Cref{sec:conclusions} concludes with proposed avenues for further research.

@@

    Now that the notion of a causal structure $\graph$ is defined along with some standard graph-theoretic notation, it is now possible to precisely define the notion of compatibility between $\graph$ and a probability distribution $\prob[\nodes]$ defined over the nodes of $\graph$. Intuitively, the absence of certain causal connections within $\graph$ should limit the set of possible observations that can be made on $\graph$. Specifically, the causal structure $\graph$ hypothesizes that each variable $n \in \nodes$ is causally influenced by its parents $\Pa[\graph]{n}$, then $n$ should be independent of all other variables, except its own descendants when conditioned over $\Pa[\graph]{n}$. This is known as the \term{local Markov property}:\footnote{Here $A \indep B \mid C$ denotes statistical independence between $A$ and $B$ conditional on $C$ where $A,B,C \subseteq \nodes$, i.e. for a given probability distribution $\prob[\nodes]$, $\prob[AB \mid C] = \prob[A \mid C]\prob[B \mid C]$.}
    \[ n \indep \br{\nodes \setminus \De[\graph]{n}} \mid \Pa[\graph]{n} \quad \forall n \in \nodes \eq \label{eq:local_markov_property} \]
    If a given distribution $\prob[\nodes]$ defined over \textit{all} of the nodes $\nodes$ of $\graph$ satisfies \cref{eq:local_markov_property}, then $\prob[\nodes]$ is said to be \term{compatible with $\graph$}. Alternatively yet equivalently, the notion of compatibility can be interpreted as follows: a distribution $\prob[\nodes]$ is compatible with $\graph$ if $\prob[\nodes]$ can be consistently factorized into conditional probability distributions for each variable $n \in \nodes$ conditioned on its parents $\Pa[\graph]{n}$:
    \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}] \eq \label{eq:local_markov_property_operation}\]
    The conditional distributions in \cref{eq:local_markov_property_operation} (i.e. $\{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes\}$) are referred to as a set of \term{causal parameters for $\graph$}. If a distribution $\prob[\nodes]$ violates \cref{eq:local_markov_property} or equivalently cannot be factorized according to \cref{eq:local_markov_property_operation}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$. When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is trivially easy to verify whether or not $\prob[\nodes]$ is compatibility with $\graph$; \cref{sec:satisfaction_of_d_sep_relations} describes in detail how this is accomplished.

    A challenge is present when one is supplied with a partial observation, i.e. a joint distribution $\prob[\nodes_{O}]$ where $\nodes_{O} \subset \nodes$ is some subset of variables referred to as the \term{observable nodes} $\nodes_O$. In such cases, \cref{eq:local_markov_property_operation} can not be verified by direction calculation because it is certainly possible that the parents of some observable node are themselves unobservable $\Pa[\graph]{\nodes_{O}} \not \subseteq \nodes_{O}$. In such cases, compatibility between $\graph$ and $\prob[\nodes_{O}]$ depends on the existence or non-existence of a set of causal parameters for $\graph$ such that $\prob[\nodes_{O}] = \prod_{n \in \nodes_{O}} \prob[n \mid \Pa[\graph]{n}]$. The unobservable nodes are termed \term{latent nodes} $\nodes_L = \nodes \setminus \nodes_{O}$ representing hidden random variables that are hidden either by some fundamental process or cannot be measured due to other limitations.
    \todo[TC]{Explain why this is difficult more.}
    \todo[TC]{Figure out if I should include d-sep here}
    \todo[TC]{Explain what this work and inflation accomplishes regarding this}

@@

    \section{Triangle Structure}
    \label{sec:triangle_structure}

    \begin{figure}
    \begin{center}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
            \caption{The Bell structure consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively. The shared hidden variable is labeled $\la$.}
            \label{fig:bell_scenario}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
            \caption{The casual structure of the Triangle structure. Three variables $A,B,C$ are observable, while $X, Y, Z$ are latent variables.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{center}
    \end{figure}
    Discovering quantum non-classicality in any causal structure is desirable, so why, in particular, is it important to do so in the Triangle structure? As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{Triangle structure} (\cref{fig:triangle_structure}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.

    Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the Triangle structure if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that
    %the joint distribution $\prob[\nodes] = \prob[ABCXYZ]$ is a product over the causal parameters,
    %\[ \prob[ABCXYZ] = \prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
    %And also, the given distribution
    $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$:
    \[ \prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \eq \label{eq:triangle_compatibility} \]

    For certain causal structures, the conditional independence relations provided by $d$-separation relations are a sufficient characterization of compatibility. Recently, \citet{Henson_2014}, classified the Triangle structure as an \textit{interesting} causal structure in the sense that conditional independence relations \textit{do not} provide a sufficient characterization of non-classicality.\footnote{Note that the Triangle structure possesses \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Moreover, \citet{Inflation} concretely demonstrate that the space of classical distributions on the Triangle structure is non-convex, unlike the Bell structure. It can be argued that convexity of the Bell structure distributions is partially responsible for the wealth of knowledge that is known about the Bell structure. It is also reasonable to speculate that quantum non-classicality in the triangle can be translated directly into a computational advantage for certain computational circuits~\cite{Terhal_2002}. Characterizing quantum non-classicality for interesting causal structures remains an unsolved problem, and the Triangle structure is a small, non-trivial case study.

    Additionally, \citet{Fritz_2012} demonstrated that the Triangle structure is the \textit{smallest} correlation scenario\footnote{Correlation scenarios differ from the Bell structure in that measure setting variables are non-existent in correlation scenarios.} in which their exists incompatible, quantum distributions by explicitly mentioning one which we have elected to call the Fritz distribution (see \cref{sec:fritz_distribution}). Fritz's proof of non-classicality does not involve compatibility inequalities, but instead mentions that inequalities would be helpful for characterizing non-classical in the Triangle structure.
    \comment[E]{Revisions processed up to here thusfar.}

    Finally \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:inflation_technique}), a novel tool for solving causal inference problems. Using the inflation technique, they were able to prove incompatibility between the Triangle structure and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints. Therefore as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the Triangle structure that all others.

    It is worth noting that a number of causal compatibility inequalities for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality for a series of causal structures with $n \in \N$ variables where at most $c \in \N$ share a common ancestor. The Triangle structure is a special case with $c = 2$, $n = 3$. Moreover, \citet{Henson_2014} derive a family of entropic inequalities constraining the set of compatible correlations. Most impressively, \citet{Inflation} derive a family of polynomial, $2$-outcome, causal compatibility inequalities; $37$ non-trivial representatives are printed in~\cite{Inflation}.

    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by \citet{Henson_2014}. Unfortunately, none of these inequalities could be violated. These early results suggest, although do not prove, that quantum non-classical does not exist in the Triangle structure for \textit{two-outcome} measurements. It is therefore conjectured that all quantum non-classical distributions in the Triangle structure utilize more than $2$ outcomes in at least one party. Moreover we take these observations as motivation to explore incompatibility in Triangle structure for a larger cardinalities.

@@

    Here the notation $\prob[\fritz][abc] = \prob[\p{ABC}][abc] = \prob[][\p A=a,\p B=b,\p C=c]$ is used as shorthand. The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:quantum_model_triangle}~\cite{Fritz_2012}. The Fritz distribution is best visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}. From this diagram, it can be seen that each of $\p{C}$'s outcomes restricts the possible outcomes for $\p A,\p B$ into a $2 \times 2$ block. If one writes the outcome labels $\bc{0,1,2,3}$ in binary $\bc{00,01,10,11}$, it can be seen that the left-hand bits for $\p A$ and $\p B$ (respectively denoted $\p A_l$, $\p B_l$) are fixed by the outcome of $\p C$. Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded} the left-hand bits emulate the measurement settings $S_{\p A}$ and $S_{\p B}$ and the right-hand bits emulate a two-outcome measurement performed by $A, B$ as they would in~\cref{fig:bell_scenario}. Specifically, $\p C$'s bits are perfectly correlated with the left-bits of $A,B$; $\p C_l = \p A_l$ and $\p C_r = \p B_l$.

@@

    % The shared resource between $A$ and $B$ (graphically denoted $\la$ in \cref{fig:triangle_structure_with_fritz_bell_embedded}) is the maximally entangled Bell state:
    % \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \qquad \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \]
    % While the states shared with $C$ are the following mixed states:
    % \[ \rho_{BC} = \rho_{CA} = \f{\ket{00}\bra{00} + \ket{11}\bra{11}}{2} \]
    % The measurements employed by $A,B$ and $C$ are separable, projective measurements,
    % \begin{align*}
    %     M_{A} &= \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
    %     M_{B} &= \bc{\ket{\psi_{6}0}\bra{\psi_{6}0}, \ket{\psi_{2}0}\bra{\psi_{2}0}, \ket{\psi_{0}1}\bra{\psi_{0}1}, \ket{\psi_{4}1}\bra{\psi_{4}1}} \\
    %     M_{C} &= \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
    % \end{align*}
    % Where $\ket{\psi_n}$ is shorthand for,
    % \[ \ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}} \]
    % Using the above states and measurements, the Fritz distribution $\prob[\fritz]$ can be recovered using the following:
    % \[ \prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}} \]
    % Where $\netperm$ is a $64 \times 64$ permutation matrix to be elaborated in \cref{sec:perm_matrix}.
    % Moreover, the quantum implementation of the Fritz distribution presented above is non-unique also. For example, it is possible to implement the Fritz distribution using maximally entangled Bell states for each shared resource  provided there is an appropriate adjustment to the measurements . Ultimately however, only $\rho_{AB}$ is required to be entangled in order to reproduce the Fritz; after-all, $C$ is simply classically announcing $A_r$ and $B_r$ as he receives them.

    It is important to understand the domain in which Fritz's proof of incompatibility is valid; the details of which can found in the original work~\cite{Fritz_2012}. Specifically, \cref{eq:CHSH_intriangle} only acts as a valid causal compatibility inequalty for the Triangle structure if there exists perfect correlation between $\p C$'s outcomes and the measurement pseudo-settings (left-bits) of $\p A$ and $\p B$. As a result, the incompatibility proof employed by Fritz is not applicable to any distribution that significantly deviates from the Fritz distribution presented above. For example, if one combines \cref{eq:fritz_dist} with more and more uniform noise, at what point does the resultant distribution transition from incompatibility to compatibility? This question is partially answered in \cref{sec:noise}.

@@

    Equipped with the Fritz distribution (\cref{sec:fritz_distribution}) and the inflation technique (\cref{sec:inflation_technique}), it is now possible to derive causal compatibility inequalities for the triangle that are violated by the Fritz distribution; the procedure for doing so is as follows. First select an inflation $\graph'$ of the Triangle structure $\graph$ and identify the maximal pre-injectable sets $\PreInj[\graph]{\graph'}$. These sets define the marginal scenario to be used in the Inflation Technique. Next, inflate the Fritz distribution into the pre-injectable sets as described by the Inflation lemma (\cref{lem:inflation}). Finally, obtain infeasibility certificates using some linear programing software and obtain a valid causal compatibility inequality that witnesses the Fritz distribution's incompatibility.

>>>>

    The manuscript is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used. \Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities. \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure is worth studying. \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}. The Fritz distribution was proven to be non-classical without the use of inequalities --- this report fills in the desired missing inequalities. A sample of these inequalities are presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq,eq:web_inequality,eq:symmetic_web_inequality}. Finally, \cref{sec:violations_noise} introduces a method for parameterizing the space of quantum-accessible distributions which we used to numerically optimize against our derived inequalities in search of stronger types of non-classicality. Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities. \Cref{sec:conclusions} concludes with proposed avenues for further research.

    \Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the specific context of this work. Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}. \Cref{sec:deriving_inequalities} demonstrates how the Inflation Technique was used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions.

@@

    Now that the notion of a causal structure $\graph$ is defined along with some standard graph-theoretic notation, it is now possible to precisely define the notion of compatibility between $\graph$ and a probability distribution $\prob[\nodes]$ defined over the nodes of $\graph$. Intuitively, the absence of certain causal connections within $\graph$ should limit the set of possible observations that can be made on $\graph$. Specifically, the causal structure $\graph$ hypothesizes that each variable $n \in \nodes$ is causally influenced by its parents $\Pa[\graph]{n}$, then $n$ should be independent of all other variables, except its own descendants when conditioned over $\Pa[\graph]{n}$. This is known as the \term{local Markov property}:\footnote{Here $A \indep B \mid C$ denotes statistical independence between $A$ and $B$ conditional on $C$ where $A,B,C \subseteq \nodes$, i.e. for a given probability distribution $\prob[\nodes]$, $\prob[AB \mid C] = \prob[A \mid C]\prob[B \mid C]$.}
    \[ n \indep \br{\nodes \setminus \De[\graph]{n}} \mid \Pa[\graph]{n} \quad \forall n \in \nodes \eq \label{eq:local_markov_property} \]
    If a given distribution $\prob[\nodes]$ defined over \textit{all} of the nodes $\nodes$ of $\graph$ satisfies \cref{eq:local_markov_property}, then $\prob[\nodes]$ is said to be \term{compatible with $\graph$}. Alternatively yet equivalently, the notion of compatibility can be interpreted as follows: a distribution $\prob[\nodes]$ is compatible with $\graph$ if $\prob[\nodes]$ can be consistently factorized into conditional probability distributions for each variable $n \in \nodes$ conditioned on its parents $\Pa[\graph]{n}$:
    \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}] \eq \label{eq:compatibility_as_factorization}\]
    The conditional distributions in \cref{eq:compatibility_as_factorization} (i.e. $\{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes\}$) are referred to as a set of \term{causal parameters for $\graph$}. If a distribution $\prob[\nodes]$ violates \cref{eq:local_markov_property} or equivalently cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$. When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is trivially easy to verify whether or not $\prob[\nodes]$ is compatibility with $\graph$; \cref{sec:satisfaction_of_d_sep_relations} describes in detail how this is accomplished.

    A challenge is present when one is supplied with a partial observation, i.e. a joint distribution $\prob[\nodes_{O}]$ where $\nodes_{O} \subset \nodes$ is some subset of variables referred to as the \term{observable nodes} $\nodes_O$. In such cases, \cref{eq:compatibility_as_factorization} can not be verified by direction calculation because it is certainly possible that the parents of some observable node are themselves unobservable $\Pa[\graph]{\nodes_{O}} \not \subseteq \nodes_{O}$. In such cases, compatibility between $\graph$ and $\prob[\nodes_{O}]$ depends on the existence or non-existence of a set of causal parameters for $\graph$ such that $\prob[\nodes_{O}] = \prod_{n \in \nodes_{O}} \prob[n \mid \Pa[\graph]{n}]$. The unobservable nodes are termed \term{latent nodes} $\nodes_L = \nodes \setminus \nodes_{O}$ representing hidden random variables that are hidden either by some fundamental process or cannot be measured due to other limitations.
    \todo[TC]{Explain why this is difficult more.}
    \todo[TC]{Figure out if I should include d-sep here}
    \todo[TC]{Explain what this work and inflation accomplishes regarding this}

@@

    \begin{figure}
    \begin{center}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
            \caption{The Bell structure consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively. The shared hidden variable is labeled $\la$.}
            \label{fig:bell_scenario}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
            \caption{The casual structure of the Triangle structure. Three variables $A,B,C$ are observable, while $X, Y, Z$ are latent variables.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{center}
    \end{figure}
    \section{Triangle Structure}
    \label{sec:triangle_structure}

    Discovering quantum non-classicality in any causal structure is desirable, so why, in particular, is it important to do so in the Triangle structure? As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{Triangle structure} (\cref{fig:triangle_structure}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$. Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the Triangle structure if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that
    %the joint distribution $\prob[\nodes] = \prob[ABCXYZ]$ is a product over the causal parameters,
    %\[ \prob[ABCXYZ] = \prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
    %And also, the given distribution
    $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$:
    \[ \prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \eq \label{eq:triangle_compatibility} \]

    For certain causal structures, the conditional independence relations provided by $d$-separation relations are a sufficient characterization of compatibility. Recently, \citet{Henson_2014}, classified the Triangle structure as an \textit{interesting} causal structure in the sense that conditional independence relations \textit{do not} provide a sufficient characterization of non-classicality.\footnote{Note that the Triangle structure possesses \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Moreover, \citet{Inflation} concretely demonstrate that the space of classical distributions on the Triangle structure is non-convex, unlike the Bell structure. It can be argued that convexity of the Bell structure distributions is partially responsible for the wealth of knowledge that is known about the Bell structure. It is also reasonable to speculate that quantum non-classicality in the Triangle structure can be translated directly into a computational advantage for certain computational circuits~\cite{Terhal_2002}. Characterizing quantum non-classicality for interesting causal structures remains an unsolved problem, and the Triangle structure is a small, non-trivial case study.

    Additionally, \citet{Fritz_2012} demonstrated that the Triangle structure is the \textit{smallest} correlation scenario\footnote{Correlation scenarios differ from the Bell structure in that measurement setting variables are absent in correlation scenarios.} in which their exists incompatible, quantum distributions by explicitly mentioning one which we discuss in detail in \cref{sec:fritz_distribution}. Fritz's proof of non-classicality does not involve compatibility inequalities, but instead mentions that inequalities would be helpful for characterizing non-classical in the Triangle structure.
    % \comment[E]{Revisions processed up to here thusfar.}

    Finally, \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:inflation_technique}) --- a novel tool for solving causal inference problems. Using the Inflation Technique, they were able to prove incompatibility between the Triangle structure and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints. Consequently, as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the Triangle structure than all others.

    It is worth noting that a number of causal compatibility inequalities for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality for a series of causal structures with $n \in \N$ variables where at most $c \in \N$ share a common ancestor. The Triangle structure is a special case with $c = 2$, $n = 3$. Moreover, \citet{Henson_2014} derive a family of entropic inequalities constraining the set of compatible correlations. Most recently, \citet{Inflation} derive a family of polynomial, $2$-outcome, causal compatibility inequalities; $37$ non-trivial representatives are printed in~\cite{Inflation}.

    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by \citet{Henson_2014}. Unfortunately, none of these inequalities could be violated. These early results suggest, although do not prove, that quantum non-classical does not exist in the Triangle structure for \textit{two-outcome} measurements. Therefore, it is conjectured that all quantum non-classical distributions in the Triangle structure must utilize more than $2$ outcomes in at least one variable. Moreover we take these observations as motivation to explore incompatibility in Triangle structure for a larger cardinalities.

@@

    Here the notation $\prob[\fritz][abc] = \prob[\p{ABC}][abc] = \prob[][\p A\mapsto a,\p B\mapsto b,\p C\mapsto c]$ is used as shorthand. The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:quantum_model_triangle}~\cite{Fritz_2012}. The Fritz distribution is best visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}. From this diagram, it can be seen that each of $\p{C}$'s outcomes restricts the possible outcomes for $\p A,\p B$ into a $2 \times 2$ block. If one writes the outcome labels $\bc{0,1,2,3}$ in binary $\bc{00,01,10,11}$, it can be seen that the left-hand bits for $\p A$ and $\p B$ (respectively denoted $\p A_l$, $\p B_l$) are fixed by the outcome of $\p C$. Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded} the left-hand bits emulate the measurement settings $S_{\p A}$ and $S_{\p B}$ and the right-hand bits emulate a two-outcome measurement performed by $A, B$ as they would in~\cref{fig:bell_scenario}. Specifically, $\p C$'s bits are perfectly correlated with the left-bits of $A,B$; $\p C_l = \p A_l$ and $\p C_r = \p B_l$.

@@

    It is important to understand the domain in which Fritz's proof of incompatibility is valid; the details of which can found in the original work~\cite{Fritz_2012}. Specifically, \cref{eq:CHSH_intriangle} only acts as a valid causal compatibility inequality for the Triangle structure if there exists perfect correlation between $\p C$'s outcomes and the measurement pseudo-settings (left-bits) of $\p A$ and $\p B$. As a result, the incompatibility proof employed by Fritz is not applicable to any distribution that significantly deviates from the Fritz distribution presented above. For example, if one combines \cref{eq:fritz_dist} with more and more uniform noise, at what point does the resultant distribution transition from incompatibility to compatibility? This question is partially answered in \cref{sec:noise}.

@@

    \Cref{sec:causal_compatibility} defined causal compatibility inequalities while \cref{sec:fritz_distribution} recalled and discussed the Fritz distribution together with a brief summary of its incompatibility with the Triangle Structure. Heretofore, there were no known causal compatibility inequalities for the Triangle Structure that were capable of witnessing the non-classicality of any quantum distributions~\cite{Inflation}. By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle Structure that are violated by the Fritz distribution. A representative sample of these inequalities are presented here. The methods used to derive these inequalities are largely based on the Inflation Technique~\cite{Inflation}. A summary of the Inflation Technique and other methods used will be deferred to \cref{sec:inflation_technique} where unfamiliar readers will find a succinct yet sufficient presentation of the requisites.

    The first causal compatibility inequality is reported below:
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq}
    2P_{ABC}(203)P_{C}(0) + 2P_{ABC}(303)P_{C}(0) + P_{ABC}(003)P_{C}(0) + P_{ABC}(013)P_{C}(0) + \cdots \\
    \cdots + P_{ABC}(020)P_{C}(2) + P_{ABC}(022)P_{C}(2) + P_{ABC}(023)P_{C}(0) + P_{ABC}(023)P_{C}(2) + \cdots \\
    \cdots + P_{ABC}(030)P_{C}(2) + P_{ABC}(031)P_{C}(2) + P_{ABC}(032)P_{C}(2) + P_{ABC}(033)P_{C}(0) + \cdots \\
    \cdots + P_{ABC}(033)P_{C}(2) + P_{ABC}(103)P_{C}(0) + P_{ABC}(113)P_{C}(0) + P_{ABC}(123)P_{C}(0) + \cdots \\
    \cdots + P_{ABC}(133)P_{C}(0) + P_{ABC}(200)P_{C}(0) + P_{ABC}(200)P_{C}(1) + P_{ABC}(200)P_{C}(2) + \cdots \\
    \cdots + P_{ABC}(200)P_{C}(3) + P_{ABC}(201)P_{C}(0) + P_{ABC}(201)P_{C}(1) + P_{ABC}(201)P_{C}(2) + \cdots \\
    \cdots + P_{ABC}(201)P_{C}(3) + P_{ABC}(203)P_{C}(1) + P_{ABC}(203)P_{C}(2) + P_{ABC}(203)P_{C}(3) + \cdots \\
    \cdots + P_{ABC}(213)P_{C}(0) + P_{ABC}(223)P_{C}(0) + P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + \cdots \\
    \cdots + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) + P_{ABC}(301)P_{C}(0) + P_{ABC}(301)P_{C}(1) + \cdots \\
    \cdots + P_{ABC}(301)P_{C}(2) + P_{ABC}(301)P_{C}(3) + P_{ABC}(302)P_{C}(1) + P_{ABC}(303)P_{C}(1) + \cdots \\
    \cdots + P_{ABC}(303)P_{C}(2) + P_{ABC}(303)P_{C}(3) + P_{ABC}(313)P_{C}(0) - P_{ABC}(000)P_{C}(3) \geq 0
    \end{gathered}
    \end{equation*}
    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle Structure (i.e. factorizes according to \cref{eq:compatibility_as_factorization}) must satisfy \cref{eq:ww_ineq}. As a demonstration, the Fritz distribution violates \cref{eq:ww_ineq}. Notice the final term $\prob[ABC]\br{000}\prob[C]\br{3}$ has a coefficient $-1$. For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms in \cref{eq:ww_ineq} sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $-0.0129\ldots \not \geq 0$. Consequently we conclude that the Fritz distribution is incompatible with the Triangle Structure, a fact that was previously only demonstrated without the use of causal compatibility inequalities.

    It is possible to simplify \cref{eq:ww_ineq} identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$. Upon doing so, one obtains the following,
    \begin{gather*}
        P_{ABC}(303)P_{C}(0) + P_{ABC}(313)P_{C}(0) + P_{ABC}(302)P_{C}(1) + P_{AB}(02)P_{C}(2) + P_{AB}(03)P_{C}(2) + \cdots \\
        \cdots + P_{AB}(20) + P_{AB}(30) + P_{C}(3)P_{C}(0) - P_{ABC}(000)P_{C}(3) - P_{ABC}(021)P_{C}(2) + \cdots \\
        \cdots - P_{ABC}(202) - P_{ABC}(302) - P_{ABC}(233)P_{C}(0) - P_{AC}(33)P_{C}(0) \geq 0
    \end{gather*}
